Modelling the Retinotectal projection - can competition provide a stopping mechanism?

### 2022-03-01 paper/paper.tex
Adds single axon inkscape figure
Small changes to manuscript

The model defined by the receptor and ligand expressions of Eqs.\,\ref{e:retrcpt}
\& \ref{e:tecligexp} along with Eq.\,\ref{e:mv2} has three
free parameters; $m_{\!_G}$, $m_c$ and $r_c$. To find the best combination of
these parameters, we reasoned that evolution would optimize the arrangement of
the wildtype pattern. We performed a simulated annealing optimization to
minimize the error metric, $\epsilon$, for the wildtype pattern
(Fig.\,\ref{f:G}E) at simulation time 1000. The parameters returned were
$m_{\!_G}$ = 0.003841, $m_c$ = 0.09959 and $r_c$ = 0.39918. Fig.\,\ref{f:GC}
shows the $\mathbf{GC}$ simulation with these parameters. Fish net plots at
$t=40$ and $t=1000$ show that the pattern develops quickly and compares well
with the expected layout (Fig.\,\ref{f:G}E). We investigated the response of
this model to the same set of surgical manipulations shown for the
chemoaffinity-only model in Fig.\,\ref{f:Gsurg}. We confirmed that the
addition of competition leads to a better correspondence to the experimental
results than for the chemoaffinity-only model (see supplementary
Fig.\,\ref{f:GCsurg}).

@@

Because the competition effect, $\mathbf{C}_b$ (Eq.\,\ref{e:C}), requires a
global supervisor to provide information to each branch about the location of
all other branches (But \textbf{fixme}, arguably, so does the GJ model now!),
we looked for a receptor-ligand interaction that could signal between axon
branches and enable them to adjust their movements away from one another.

@@

@@

>>>>

The model defined by the receptor and ligand expressions of Eqs.\,\ref{e:retrcpt}
\& \ref{e:tecligexp} along with Eq.\,\ref{e:mv2} has three
free parameters; $m_{\!_G}$, $m_c$ and $r_c$. To find the best combination of
these parameters, we reasoned that evolution would optimize the arrangement of
the wildtype pattern. We performed a simulated annealing optimization to
minimize the error metric, $\epsilon$, for the wildtype pattern
(Fig.\,\ref{f:G}E) at simulation time 1000. The parameters returned were
$m_{\!_G}$ = 0.003841, $m_c$ = 0.09959 and $r_c$ = 0.39918. Fig.\,\ref{f:GC}
shows the $\mathbf{GC}$ simulation with these parameters. Fish net plots at
$t=40$ and $t=1000$ show that the pattern develops quickly and compares well
with the expected layout (Fig.\,\ref{f:G}E). We investigated the response of
this model to the same set of surgical manipulations shown for the
chemoaffinity-only model in Fig.\,\ref{f:Gsurg}. We confirmed that the
addition of competition leads to a better correspondence to the experimental
results than for the chemoaffinity-only model (see supplementary
Fig.\,\ref{f:GCsurg}). We also confirmed the result
from \citet{simpson_simple_2011} that this description of a competitive
interaction is not able to reproduce the result of \citet{reber_relative_2004}
(Fig.\,\ref{f:GCreber}) Hmm. DID we? That graph looks nearly as good as the GJ
one...

@@

Because the competition effect, $\mathbf{C}_b$ (Eq.\,\ref{e:C}), does not
describe a signalling mechanism and cannot, on its own, explain all of the
experimental results, we looked for a receptor-ligand interaction that could
signal between axon branches and enable them to adjust their movements away
from one another.

@@

\begin{figure}
\centering
\includegraphics[width=0.7\linewidth]{./images/single_axon.png}
\caption{ \textbf{A} Central \textbf{B} Caudal (nasal RGC) \textbf{C} Rostral
(temporal RGC)}
\label{f:single}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{./images/j4_ee_GC_best_1_reber_exit_true_steps_1500.png}
\caption{$\mathbf{GC}$ model, Reber experiment.}
\label{f:GCreber}
\end{figure}
